\boldmath Disconnected pseudo-$C_\ell$ covariances for projected large-scale structure data

### 2019-06-18 draft/paper.tex
added caption of Fig. 13 & 14

  \appendix
  \section{Flat sky}\label{app:flat}
    \begin{figure}
      \centering
      \includegraphics[width=0.6\textwidth]{./figures/mask-lss_flat1.pdf}
      \caption{\todo{write}} \label{fig:mask_flat}
    \end{figure}

    \begin{figure}
      \centering
      \includegraphics[width=\textwidth]{./figures/run_chi2_TT_TE_EE_TB_EB_BB.pdf}
      \caption{\todo{write}}
      \label{fig:chi2_1bin_flat}
    \end{figure}
    We have repeated the analysis described in Section \ref{sec:results} on flat-sky realizations, making use of the flat-sky implementation of {\tt NaMaster}. We generate Gaussian realizations of the galaxy overdensity and shear maps making use of flat-sky extensions of the methods described in Section \ref{ssec:results.sims}. In this case we use a high-resolution mask constructed from the bright-object mask distributed with the first data release of the HSC collaboration \todo{cite} for the VVDS field, which is shown in Fig. \ref{fig:mask_flat}.

>>>>

  \appendix
  \section{Flat sky}\label{app:flat}
    \begin{figure}
      \centering
      \includegraphics[width=0.6\textwidth]{./figures/mask-lss_flat1.pdf}
      \caption{Flat-sky mask used in the study of the analytical
        methods presented in this work in the flat-sky regime. The mask was
        constructed from the bright-object mask distributed with the first
        data release of the HSC collaboration \todo{cite} for the VVDS
        field. As in the full-sky case, it is used both for galaxy clustering
        and shear for simplicity.} \label{fig:mask_flat}
    \end{figure}

    \begin{figure}
      \centering
      \includegraphics[width=\textwidth]{./figures/run_chi2_TT_TE_EE_TB_EB_BB.pdf}
      \caption{$\chi^2$ distributions for the autocorrelations of the fields
        of a redshift bin in the flat-sky regime. We compare the distributions
        obtained with the covariance matrix estimated from simulated power
        spectra, and the analytical NKA and Spin-0 methods. In addition, we
        show the theoretical $\chi^2$ distribution, which is almost perfectly
        followed by the others. The reason why the E and B modes are well
        behaved in flat sky is because in this regime ($\ell \in (120,
        17640)$), the shear power spectra is dominated by noise (see
        Fig.~\ref{fig:cl-2bins}). }
      \label{fig:chi2_1bin_flat}
    \end{figure}
    We have repeated the analysis described in Section \ref{sec:results} on flat-sky realizations, making use of the flat-sky implementation of {\tt NaMaster}. We generate Gaussian realizations of the galaxy overdensity and shear maps making use of flat-sky extensions of the methods described in Section \ref{ssec:results.sims}. In this case we use a high-resolution mask constructed from the bright-object mask distributed with the first data release of the HSC collaboration \todo{cite} for the VVDS field, which is shown in Fig. \ref{fig:mask_flat}.
